Commutative character sheaves and geometric types for supercuspidal representations

### 2017-04-06 Geometric types.tex
Corollary 3.2 needed very little work.

\begin{proof}
As above, we set $H=G\der$
and let $j : H\hookrightarrow G$ be the inclusion. 
With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
& \CSab(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]

Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ in $\CS(H)$.
Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
Applying the forgetful functor $\CS_H(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.

Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{H}$ in $\CS(H)$.
\end{proof}

>>>>

\begin{proof}
Notation as above.
Consider the following diagram.
%\[
%\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
%\end{tikzcd}
%\]
%gives
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q\ab^*} \\
& \CSab(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]

Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$.
Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
Applying the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.

Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
\end{proof}
